Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-10-31 analysis/paper/paper.qmd
update a few more places where cv is calculated, change output of fn from % to 0-1 value

# use this one that is optimized for small samples

mccv <- function(x, ... ) sd(x, ...) / mean(x, ...) * 100 * (1 + 1/(4*length(x)))

@@

cv_by_full_site_df_label <-
  df_full_sitename %>%
  dplyr::select(-SPstage.Stage) %>%
  group_by(full_sitename) %>%
  add_tally() %>%
  dplyr::filter( n > 1) %>%
  mutate(label = as.factor(paste0(full_sitename,' (N = ', n, ")"))) %>%
  dplyr::select(-n) %>%
  nest(-full_sitename, -label) %>%
  dplyr::mutate(cv_by_site = purrr::map(data, ~map_df(.x, cv))) %>%
  dplyr::select(-cv_by_site)

@@

######CV for per raw materials (n=X) with the full site name : label
cv_by_raw_materials_df_label <-
  df_sitename %>%
  group_by(SPstage.Raw_material) %>%
  add_tally() %>%
  dplyr::filter( n > 1) %>%
  mutate(label = as.factor(paste0(SPstage.Raw_material,' (N = ', n, ")"))) %>%
  dplyr::select(-n) %>%
  nest(-SPstage.Raw_material, -label) %>%
  mutate(cv_by_site = purrr::map(data, ~map_df(.x, cv))) %>%
  dplyr::select (-cv_by_site)

>>>>

# use this one that is optimized for small samples, returns value 0-1, not %

mccv <- function(x, ... ) sd(x, ...) / mean(x, ...) * (1 + 1/(4*length(x)))

@@

cv_by_full_site_df_label <-
  df_full_sitename %>%
  dplyr::select(-SPstage.Stage) %>%
  group_by(full_sitename) %>%
  add_tally() %>%
  dplyr::filter( n > 1) %>%
  mutate(label = as.factor(paste0(full_sitename,' (N = ', n, ")"))) %>%
  dplyr::select(-n) %>%
  nest(-full_sitename, -label) %>%
  dplyr::mutate(cv_by_site = purrr::map(data, ~map_df(.x, mccv))) %>%
  dplyr::select(-cv_by_site)

@@

######CV for per raw materials (n=X) with the full site name : label
cv_by_raw_materials_df_label <-
  df_sitename %>%
  group_by(SPstage.Raw_material) %>%
  add_tally() %>%
  dplyr::filter( n > 1) %>%
  mutate(label = as.factor(paste0(SPstage.Raw_material,' (N = ', n, ")"))) %>%
  dplyr::select(-n) %>%
  nest(-SPstage.Raw_material, -label) %>%
  mutate(cv_by_site = purrr::map(data, ~map_df(.x, mccv))) %>%
  dplyr::select (-cv_by_site)
